### 2017-02-02 thesis/latex/thesis.tex
Add few numbers from Weihong's paper to thesis.

\begin{itemize}
\item How dynein is a structure which turns chemical energy into motion
\item How it's weird that a cellular structure can generate directed motion
\item Other cool stuff - make dynein mysterious and cool.
\end{itemize}

@@

>>>>

\begin{itemize}
\item How dynein is a structure which turns chemical energy into motion
\item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
\item How it's weird that a cellular structure can generate directed motion
\item Other cool stuff - make dynein mysterious and cool.
\end{itemize}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c |}
    \hline
    Author & Conditions & Velocity & Run length\\\hline
    Qiu \cite{weihongpaper} & 1mM [ATP] & $134 \pm 60.4$ nm & $1.06 \pm 0.044 \mu m$\\ \hline
    Reck-Peterson \cite{reck2006single} & 1mM [ATP] & $85 \pm 30 nm/s$  & $1.9 \pm 0.2 \mu m$\\ \hline
  \end{tabular}
  \caption{Table of literature values for dynein behavior}
  \label{table:parameter-table}
\end{figure}
